---
title: "ReproHack"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary
## OSF

- there should be a license
- the OSF project is publicly available
- the folder structure is very clear (data and analysis are separated)
- the OSF project did not have any explanation in the Wiki

## Analysis

- the JASP output could be added, together with the already present pdf
- there are both xlsx and csv. to avoid redundancy and confusion, better keep only csv
- **R Script PDR1.R**
    - improve readability: maybe use `styler`?
    - the code does not point to the data
        - solutions: add correct absolute path, use package `here` with Rprojects
    - comment out `install.packages`
    - there is no data wrangling script. In other words, how was the "Final_Data" file produced from the "Raw_Data"? Although the process is described in the codebook, it would be nicer to document it as code.
    - better documentation is needed for both analyses
    - first analysis: means and SDs not reproduced, results not reproduced not only because of different numbers, but also because of a possible discrepancy in the statistical analysis (Wilcoxon signed rank in code, t-test in paper)
    - second analysis: we were able to fully reproduce the results
    - exploratory analysis: data cleaning commented out and confusing to follow, last exploratory analysis must be conducted on unfiltered dataset (but unclear in procedure)
        - clear environment, rerun data loading, rerun all confirmatory analysis on new (filtered) dataset

# Annotated code

##  Loading data

It'd be nice to separate installation from loading and comment out installation in case the person running the code doesn't want the package.

```{r}
# # install libraries
# install.packages("effsize")
# install.packages("ltm")
# install.packages("psych")

# load libraries
library(effsize)
library(ltm)
library(psych)
```

Authors wrote `read.csv2("Final_Data_PDR1.csv", header = TRUE)`, but it should actually be `read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)`

```{r}
# load data
data <- read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"
```

## Demographics

It might be a good idea to save calculations to variables instead of only outputting to the console.

```{r}
# the total sample
total_N <- nrow(data)
```

Calculation participants to exclude based on `data$Exclusion`. Again, if it needs to be reported in the manuscript, better to save it as variable

```{r}
excluded_ppl <- nrow(data) - nrow(data[data$Exclusion == "0",])
data <- data[data$Exclusion == "0",]
n <- nrow(data)
n
```

Calculation demographics: if it needs to be reported in the manuscript, better to save it as data frame. Also, no coding of `gender` variable in the codebook (which number is male/gemale/other?).

```{r}
#demographics after exclusions
# TABLE
demographics <- data.frame(
    gender = t(prop.table(table(data$Gender)))
)
    
prop.table(table(data$Gender))
mean(data$Age, na.rm = TRUE)
sd(data$Age, na.rm = TRUE)
sum(data$TP == "1")
sum(data$TP == "0")

```


##  Preregistered analyses

Means, SDs, and analysis results don't match the reported results

```{r}
#Effect of time pressure on reported die roll outcome
# no time pressure
SP <- data[data$TP == "0",]$Reported.outcome 
mean_sp <- mean(SP)
sd_sp <- sd(SP)

# time pressure
TP <- data[data$TP == "1",]$Reported.outcome 
mean_tp <- mean(TP)
sd_tp <- sd(TP)

# analysis
W <- wilcox.test(SP,TP,"less")
W
-qnorm(W$p.value)
rbc <- biserial.cor(data$Reported.outcome, data$TP)
rbc
r.test(n=n, r12=rbc, twotailed = FALSE)
```

These findings are reproduced

```{r}
# Was there cheating?
# time pressure
nrow(data[data$TP == "1",])
chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nTP <- sum(data$TP == "1")
Vtp <- sqrt(chi2/nTP*1)
Vtp

# no time pressure
nrow(data[data$TP == "0",])
chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nSP <- sum(data$TP == "0")
Vsp <- sqrt(chi2/nSP*1)
Vsp
```


## Exploratory analyses

### with exclusions

```{r}
#time pressure manipulation check
rtSP = data[data$TP == "0",]$Response.time
rtTP = data[data$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
rtSP = data[data$TP == "0" & data$Response.time<maxSP,]$Response.time
rtTP = data[data$TP == "1" & data$Response.time<maxTP,]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)
```

```{r}
#Self-report ratings
prop.table(table(data$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data$What.is.the.chance.that.you.will.get.the.reward.)
sd(data$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))
```

### without exclusions

```{r}
# reload data such that none of the data is excluded
data <- read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"
```

```{r}
#time pressure manipulation check
rtSP = data[data$TP == "0",]$Response.time
rtTP = data[data$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
rtSP = data[data$TP == "0",]$Response.time
rtTP = data[data$TP == "1",]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)
```


```{r}
#Self-report ratings
prop.table(table(data$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data$What.is.the.chance.that.you.will.get.the.reward.)
sd(data$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))
```