---
title: "ReproHack"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## OSF

- there should be a license
- the OSF project is publicly available
- the folder structure is very clear (data and analysis are separated)
- the OSF project did not have any explanation in the Wiki

# Analysis


- the JASP output could be added, together with the already present pdf
- they share xlsx and csv... to avoid redundancy and confusion, better keep only csv
- **R Script PDR1.R**
    - improve readability: maybe use `styler`?
    - the code does not point to the data
        - solutions: add correct absolute path, use package `here`, or Rprojects
    - comment out `install.packages`
    - no data wrangling script
    - first analysis: better documentation needed, means and SDs not reproduced, results not reproduced not only because of different numbers, but also because of a possible discrepancy in the statistical analysis (Wilcoxon signed rank in code, t-test in paper)
    - second analysis: better documentation needed, fully reproduced
    - exploratory analysis: data cleaning commented out and confusing to follow, last exploratory analysis must be conducted on unfiltered dataset (but unclear in procedure)
        - clear environment, rerun data loading, rerun all confirmatory analysis on new (filtered) dataset




It'd be nice to separate installation from loading and comment out installation in case the person running the code doesn't want the package.
```{r original}

# # install libraries
# install.packages("effsize")
# install.packages("ltm")
# install.packages("psych")

# load libraries
library(effsize)
library(ltm)
library(psych)
```

Authors wrote `read.csv2("Final_Data_PDR1.csv", header = TRUE)`, but it should actually be `read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)`

```{r}
# load data
data <- read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)
```


Save results of interest in variables instead of simply outputting them
```{r}
# the total sample
total_N <- nrow(data)

```

Calculation participants to exclude based on `data$Exclusion`. If it needs to be reported in the manuscript, better to save it as variable

```{r}
excluded_ppl <- nrow(data) - nrow(data[data$Exclusion == "0",])
```

```{r}
data <- data[data$Exclusion == "0",]
n <- nrow(data)
n
```

Calculation demographics: if it needs to be reported in the manuscript, better to save it as data frame. Also, no coding of `gender` variable in the codebook (which number is male/gemale/other?).

```{r}

#demographics after exclusions
# TABLE
demographics <- data.frame(
    gender = t(prop.table(table(data$Gender)))
)
    


prop.table(table(data$Gender))
mean(data$Age, na.rm = TRUE)
sd(data$Age, na.rm = TRUE)
sum(data$TP == "1")
sum(data$TP == "0")

```














###################################
###   Preregistered analyses    ###
###################################

#Effect of time pressure on reported die roll outcome
SP <- data[data$TP == "0",]$Reported.outcome # no time pressure 
mean(SP)
sd(SP)
TP <- data[data$TP == "1",]$Reported.outcome # time pressure
mean(TP)
sd(TP)
W <- wilcox.test(SP,TP,"less")
W
-qnorm(W$p.value)
rbc <- biserial.cor(data$Reported.outcome, data$TP)
rbc
r.test(n=n, r12=rbc, twotailed = FALSE)

#Was there cheating?
nrow(data[data$TP == "1",])
chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nTP <- sum(data$TP == "1")
Vtp <- sqrt(chi2/nTP*1)
Vtp
nrow(data[data$TP == "0",])
chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nSP <- sum(data$TP == "0")
Vsp <- sqrt(chi2/nSP*1)
Vsp








```


```{r ReproHack}


#Read in data from csv file and download needed packages
data <- read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"
#install.packages("effsize")
library(effsize)
#install.packages("ltm")
library(ltm)
#install.packages("psych")
library(psych)




```








