---
title: "ReproHack2019 (Leiden) - Reproducing Van der Cruyssen et al."
date: '`r Sys.Date()`'
author: "[Antonio Schettino](https://twitter.com/asch3tti) and [Eirini Zormpa](https://twitter.com/eirini_zormpa)"
output:
  html_document:
    theme: united
    highlight: tango
    code_folding: show
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup-report, include = FALSE}

# # uncomment if installation is required and desired 
# # install libraries
# install.packages("knitr")
# install.packages("here")

# load libraries
library(knitr)
library(here)

# for RMarkdown
options(digits = 3) # number of decimal digits
opts_chunk$set(
  warning = FALSE, # no package warnings
  message = FALSE # no package messages
)

```

Preprint accessed on Jan. 30th 2020 from [OSF Preprints](https://osf.io/qbk6z/). Materials accessed on Jan. 30th 2020 from [OSF](https://osf.io/xwzpc/).

# Original script
Below is the original script. The file is available locally at `r here("authors_materials_OSF/Analysis/R Script PDR1.R")` -- note that the absolute path will depend on where the R project file is located, but if the structure of the project folder remains the same, R will be able to read the file!

```{r original-script, eval = FALSE}

###################################
###        Loading data         ###
###################################

#Read in data from csv file and download needed packages
data <- read.csv2("Final_Data_PDR1.csv", header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"
install.packages("effsize")
library(effsize)
install.packages("ltm")
library(ltm)
install.packages("psych")
library(psych)


################################
###   Exploratory analyses   ###
################################

#without any exclusions
#omit lines 36-40 and 96-97 and include 99-100

#The subsample that expressed (strong) belief in the payment scheme
#for this exploratory analysis, we only removed the hastag from line 26, the rest of the script remained the same
#data <- data[data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game. == "Believe" | data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game. == "Strongly believe",]


##################################
###        Demographics        ###
##################################

#the total sample
nrow(data)

#exclude participants of time pressure condition who failed to report within the time limit, omit these lines for Exploratory analysis without exclusions
nrow(data) - nrow(data[data$Exclusion == "0",]) 
data <- data[data$Exclusion == "0",]
n <- nrow(data)
n

#demographics after exclusions
prop.table(table(data$Gender))
mean(data$Age, na.rm = TRUE)
sd(data$Age, na.rm = TRUE)
sum(data$TP == "1")
sum(data$TP == "0")


###################################
###   Preregistered analyses    ###
###################################

#Effect of time pressure on reported die roll outcome
SP <- data[data$TP == "0",]$Reported.outcome
mean(SP)
sd(SP)
TP <- data[data$TP == "1",]$Reported.outcome
mean(TP)
sd(TP)
W <- wilcox.test(SP,TP,"less")
W
-qnorm(W$p.value)
rbc <- biserial.cor(data$Reported.outcome, data$TP)
rbc
r.test(n=n, r12=rbc, twotailed = FALSE)

#Was there cheating?
nrow(data[data$TP == "1",])
chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nTP <- sum(data$TP == "1")
Vtp <- sqrt(chi2/nTP*1)
Vtp
nrow(data[data$TP == "0",])
chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nSP <- sum(data$TP == "0")
Vsp <- sqrt(chi2/nSP*1)
Vsp

###################################
###    Exploratory analyses     ###
###################################

#time pressure manipulation check
rtSP = data[data$TP == "0",]$Response.time
rtTP = data[data$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
rtSP = data[data$TP == "0" & data$Response.time<maxSP,]$Response.time
rtTP = data[data$TP == "1" & data$Response.time<maxTP,]$Response.time
#Exporatory analysis without exclusions: use lines 99-100 instead of 96-97
#rtSP = data[data$TP == "0",]$Response.time
#rtTP = data[data$TP == "1",]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)

#Self-report ratings
prop.table(table(data$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data$What.is.the.chance.that.you.will.get.the.reward.)
sd(data$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))

```

# Suggestions
We go through each section, provide some suggestions related to style and ease of readability, and try to reproduce the results.

## Loading data

```{r original-script-load-data, eval = FALSE}

###################################
###        Loading data         ###
###################################

#Read in data from csv file and download needed packages
data <- read.csv2("Final_Data_PDR1.csv", header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"
install.packages("effsize")
library(effsize)
install.packages("ltm")
library(ltm)
install.packages("psych")
library(psych)

```

### Comments

We recommend the following:

* begin with package installation and loading (better to comment out package installation, in case the person running the code does not want the package or already has it)

```{r comment-libraries}

# # uncomment if installation is required and desired 
# # install libraries
# install.packages("effsize")
# install.packages("ltm")
# install.packages("psych")

# load libraries
library(effsize)
library(ltm)
library(psych)

```

* load the data
    * authors wrote `read.csv2("Final_Data_PDR1.csv", header = TRUE)` but, according to their folder structure, it should be `read.csv2("Data/Final_Data_PDR1.csv", header = TRUE)`
    * to increase reproducibility, better to use _R Projects_ and locate files using the `here` package (see example below)
    * better to integrate the codebook (available at `r here("authors_materials_OSF/Codebook PDR1.pdf")`) within the analysis script, to help replicators understand the data. To easily create codebooks with rich metadata that can be easily shared online, see also the R package [`codebook`](https://github.com/rubenarslan/codebook).

```{r comment-load-data}

# load data
data <- read.csv2(here("authors_materials_OSF/Data/Final_Data_PDR1.csv"), header = TRUE)
data$Response.time <- as.numeric(as.character(data$Response.time))
names(data)[1] <- "Reported.outcome"

```

## Demographics

```{r original-script-demographics, eval = FALSE}

##################################
###        Demographics        ###
##################################

#the total sample
nrow(data)

#exclude participants of time pressure condition who failed to report within the time limit, omit these lines for Exploratory analysis without exclusions
nrow(data) - nrow(data[data$Exclusion == "0",]) 
data <- data[data$Exclusion == "0",]
n <- nrow(data)
n

#demographics after exclusions
prop.table(table(data$Gender))
mean(data$Age, na.rm = TRUE)
sd(data$Age, na.rm = TRUE)
sum(data$TP == "1")
sum(data$TP == "0")

```

### Comments

We recommend the following:

* if the results of these calculations need to be reported in the manuscript, better to save them to variables instead of only outputting to console

```{r comment-demographics1}

# the total sample
total_N <- nrow(data)
total_N

#exclude participants of time pressure condition who failed to report within the time limit, omit these lines for Exploratory analysis without exclusions
excluded_ppl <- nrow(data) - nrow(data[data$Exclusion == "0",])
excluded_ppl

data <- data[data$Exclusion == "0",]
n <- nrow(data)
n

```

* demographics after exclusion: if it needs to be reported in the manuscript, better to save it as data frame
    * no coding of `gender` variable in the codebook (which number is male/female/other?)
    * variable name `TP` is unclear, including the codebook would help (see comment above)
* we **successfully** replicated the demographics results reported in the manuscript (p. 7)

```{r comment-demographics2}

#demographics after exclusions
demographics <- data.frame(
    gender = t(prop.table(table(data$Gender)))
)

gender_prop <- prop.table(table(data$Gender))
mean_age <- mean(data$Age, na.rm = TRUE)
sd_age <- sd(data$Age, na.rm = TRUE)
TP_1 <- sum(data$TP == "1")
TP_2 <- sum(data$TP == "0")

gender_prop
mean_age
sd_age
TP_1
TP_2

```

## Preregistered Analyses

```{r original-script-preregistered-analyses, eval = FALSE}

###################################
###   Preregistered analyses    ###
###################################

#Effect of time pressure on reported die roll outcome
SP <- data[data$TP == "0",]$Reported.outcome
mean(SP)
sd(SP)
TP <- data[data$TP == "1",]$Reported.outcome
mean(TP)
sd(TP)
W <- wilcox.test(SP,TP,"less")
W
-qnorm(W$p.value)
rbc <- biserial.cor(data$Reported.outcome, data$TP)
rbc
r.test(n=n, r12=rbc, twotailed = FALSE)

#Was there cheating?
nrow(data[data$TP == "1",])
chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nTP <- sum(data$TP == "1")
Vtp <- sqrt(chi2/nTP*1)
Vtp
nrow(data[data$TP == "0",])
chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nSP <- sum(data$TP == "0")
Vsp <- sqrt(chi2/nSP*1)
Vsp

```

### Comments

```{r comment-preregistered-analyses1}

#Effect of time pressure on reported die roll outcome
# no time pressure
SP <- data[data$TP == "0",]$Reported.outcome 
mean_sp <- mean(SP)
sd_sp <- sd(SP)

# time pressure
TP <- data[data$TP == "1",]$Reported.outcome 
mean_tp <- mean(TP)
sd_tp <- sd(TP)

# analysis
W <- wilcox.test(SP,TP,"less")
W
-qnorm(W$p.value)
rbc <- biserial.cor(data$Reported.outcome, data$TP)
rbc
r.test(n=n, r12=rbc, twotailed = FALSE)

```

We **successfully** reproduced means and SDs reported in the manuscript (_Table 1_, p. 5).

We recommend the following:

* minor typo: the rank-biserial correlation is `r rbc`, whereas in the manuscript it is reported as **0.05** (_Table 1_, p. 5)
* better to save to variable all the results, e.g., also the confidence interval of _r_
* it would be good to document the applied transformation from _W_ to _Z_, as well as clarify that the lower bound of the confidence interval of the effect size _r_ is infinite -- instead of the obtained value `r r.test(n = n, r12 = rbc, twotailed = FALSE)$ci[1]` -- because the test is one-tailed

```{r comment-preregistered-analyses2}

# Was there cheating?
# time pressure
nrow(data[data$TP == "1",])
chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(TP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nTP <- sum(data$TP == "1")
Vtp <- sqrt(chi2/nTP*1)
Vtp

# no time pressure
nrow(data[data$TP == "0",])
chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
chi2 <- unname(chisq.test(table(SP), p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))$statistic)
nSP <- sum(data$TP == "0")
Vsp <- sqrt(chi2/nSP*1)
Vsp

```

We **successfully** reproduced means and SDs reported in the manuscript (_Table 1_, p. 5).

## Exploratory Analyses

```{r original-script-exploratory-analyses, eval = FALSE}

################################
###   Exploratory analyses   ###
################################

#without any exclusions
#omit lines 36-40 and 96-97 and include 99-100

#The subsample that expressed (strong) belief in the payment scheme
#for this exploratory analysis, we only removed the hastag from line 26, the rest of the script remained the same
#data <- data[data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game. == "Believe" | data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game. == "Strongly believe",]

#time pressure manipulation check
rtSP = data[data$TP == "0",]$Response.time
rtTP = data[data$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
rtSP = data[data$TP == "0" & data$Response.time<maxSP,]$Response.time
rtTP = data[data$TP == "1" & data$Response.time<maxTP,]$Response.time
#Exporatory analysis without exclusions: use lines 99-100 instead of 96-97
#rtSP = data[data$TP == "0",]$Response.time
#rtTP = data[data$TP == "1",]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)

#Self-report ratings
prop.table(table(data$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data$What.is.the.chance.that.you.will.get.the.reward.)
sd(data$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))

```

### Comments

We recommend the following:

* keep the order of the analyses consistent between the script and manuscript
* if confirmatory and exploratory datasets are different, save them separately instead of commenting/uncommenting operations (see below for an example)

```{r comment-exploratory-analyses1}

### DATA EXPLORATORY ANALYSES
# load data
data_explor <- read.csv2(here("authors_materials_OSF/Data/Final_Data_PDR1.csv"), header = TRUE)
data_explor$Response.time <- as.numeric(as.character(data_explor$Response.time))
names(data_explor)[1] <- "Reported.outcome"

```

#### Results excluding outliers

* for the self-report ratings, the sums of percentages reported in the manuscript should be calculated here as well

```{r comment-exploratory-analyses2}

#time pressure manipulation check
rtSP = data_explor[data_explor$TP == "0",]$Response.time
rtTP = data_explor[data_explor$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
rtSP = data_explor[data_explor$TP == "0" & data_explor$Response.time<maxSP,]$Response.time
rtTP = data_explor[data_explor$TP == "1" & data_explor$Response.time<maxTP,]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)

#Self-report ratings
prop.table(table(data_explor$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data_explor$What.is.the.chance.that.you.will.get.the.reward.)
sd(data_explor$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))

q1 <- prop.table(table(data_explor$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))[4]
q2 <- prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))[1] + prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))[4]
q3 <- prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))[1] + prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))[4]

```

We were **not** able to reproduce some of the results in the manuscript, although the direction of the effects is the same:

* p. 9: _"Participants in the time-pressure condition took less time to report the outcome of the die roll (M = 4.98 s, SD = 1.39 s) than those in the self-paced condition (M = 9.10 s, SD = 5.43 s), t(425) = 10.38, p < .001, d = 1.01, 95% CI [0.80, 1.21], indicating a successful time-pressure manipulation."_
* our calculations (differences in **bold**): _"Participants in the time-pressure condition took less time to report the outcome of the die roll (M = **`r mean(rtTP)`** s, SD = **`r sd(rtTP)`** s) than those in the self-paced condition (M = `r mean(rtSP)` s, SD = `r sd(rtSP)` s), t(**`r t.test(rtSP,rtTP, var.equal = TRUE)$parameter`**) = **`r t.test(rtSP,rtTP, var.equal = TRUE)$statistic`**, p < .001, d = **`r effsize::cohen.d(rtSP,rtTP)$estimate`**, 95% CI [**`r effsize::cohen.d(rtSP,rtTP)$conf.int[1]`**, **`r effsize::cohen.d(rtSP,rtTP)$conf.int[2]`**], indicating a successful time-pressure manipulation."_

#### Results including outliers

```{r comment-exploratory-analyses3}

#time pressure manipulation check
rtSP = data_explor[data_explor$TP == "0",]$Response.time
rtTP = data_explor[data_explor$TP == "1",]$Response.time
mSP <- mean(rtSP)
sdSP <- sd(rtSP)
maxSP <- mSP+5*sdSP
mTP <- mean(rtTP)
sdTP <- sd(rtTP)
maxTP <- mTP+5*sdTP
#Exporatory analysis without exclusions: use lines 99-100 instead of 96-97
rtSP = data_explor[data_explor$TP == "0",]$Response.time
rtTP = data_explor[data_explor$TP == "1",]$Response.time
mean(rtSP)
sd(rtSP)
mean(rtTP)
sd(rtTP)
t.test(rtSP,rtTP, var.equal = TRUE)
effsize::cohen.d(rtSP,rtTP)

#Self-report ratings
prop.table(table(data_explor$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))
prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))
mean(data_explor$What.is.the.chance.that.you.will.get.the.reward.)
sd(data_explor$What.is.the.chance.that.you.will.get.the.reward.)
prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))

q1 <- prop.table(table(data_explor$The.ratio.between.the.dice.roll.and.the.possible.reward.is...))[4]
q2 <- prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))[1] + prop.table(table(data_explor$My.dice.role.was.fully.anonymous.only.I.could.know.what.I.rolled.))[4]
q3 <- prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))[1] + prop.table(table(data_explor$Several.students.will.receive.a.monetary.reward.for.the.dice.under.cup.game.))[4]

```

We confirm that _"Repeating the analyses without any exclusions [...] did not alter the pattern of findings"_ (p. 9). However, we cannot verify whether results would be similar _"in the subsample that expressed (strong) belief in the payment scheme [...]"_, because no code is provided in this script.

# General Comments

## OSF

Good:

- the OSF project is publicly available
- the folder structure is clear (data and analysis are separated)

Room for improvement:

- inlcuding a license (e.g., `CC-BY 4.0`) would increase the chance of reusability
- the OSF project would benefit from an explanation of the project and files in the _Wiki_

## Analysis

Room for improvement:

- the JASP output file could be added, together with the (already present) pdf
- there are `.xlsx` and `.csv` files that, to our understanding, contain the same information. To avoid redundancy and confusion, better keep only the `.csv` file (typically preferred to Word documents, which are proprietary)
- **R Script PDR1.R**
    - it would be better to follow code conventions (e.g., be consistent when using either `=` or `<-` when assigning variables): for automatization, see the R package [`styler`](https://cran.r-project.org/web/packages/styler/vignettes/introducing_styler.html)
    - there is no data wrangling script. In other words, how was the "Final_Data" file produced from the "Raw_Data"? Although the process is described in the codebook, it would be nicer to document it as code

***
***


